The Anthropological Notation Ontology (ANNO): A core ontology for annotating human bones and deriving phenotypes

### 2023-06-06 paper.tex
continue table

% add. options: [seceqn,secthm,crcready]
\documentclass[sw]{iosart2x}
\usepackage{todonotes}
\usepackage{cleveref}
\usepackage{csquotes}
\usepackage{aurl}
%\usepackage{dcolumn}

@@

\section{Description of ANNOdc}\label{sec:core}
% Definition/Beschreibung der Kern-Konzepte/Module und -Relationen mit Beispielen, GFO-Einbettung
\begin{figure}[h]
\includegraphics[width=\textwidth]{img/core.pdf}
\caption{ANNOdc ontology}\label{fig:core}
\end{figure}

>>>>

% add. options: [seceqn,secthm,crcready]
\documentclass[sw]{iosart2x}
\usepackage{todonotes}
\usepackage{cleveref}
\usepackage{csquotes}
\usepackage{aurl}
\usepackage{booktabs}
\usepackage{tabulary}
%\usepackage{dcolumn}

@@

\section{Description and Foundation of ANNOdc}\label{sec:core}
% Definition/Beschreibung der Kern-Konzepte/Module und -Relationen mit Beispielen, GFO-Einbettung
\begin{figure}[h]
\includegraphics[width=\textwidth]{img/core.pdf}
\caption{ANNOdc ontology}\label{fig:core}
\end{figure}

\begin{table}[htbp]
  \centering
  \caption{Table Title}
  \begin{tabulary}{\textwidth}{lLLl}
    \toprule
	ANNOdc class					&Examples				&FMA equivalent / ID						&GFO superclass	\\
	\midrule
	Anatomical entity			&						&Physical anatomical entity fma61775\\
	Anatomical structure		&						&Material anatomical entity	fma67165		&Material object\\							
	Spatial anatomical entity	&						&immaterial anatomical entity fma:fma67112	&Space entity\\
	Anatomical space			&						&											&Space region\\
	Anatomical surface			&Median Plane			&Anatomical surface fma24137				&Surface region\\
	Anatomical line				&Mandibular Angle (ppam dexter-go dexter-piam dexter), Sagittal Axis&Anatomical line fma9657	&Line region\\
	Anatomical point			&Gonion					&Anatomical point							&Point region\\
	Anatomical plane			&Median Plane			&Anatomical plane fma242982\\
	Anatomical axis		 		&Sagittal Axis\\
	Skeleton					&						&Skeleton fma:fma23875\\
	Bone structure\\
	Bone						&Mandibula				&Bone organ fma:fma5018\\

	Bone part					&Protuberantia mentalis	&Related to Segment of bone organ fma:fma281808, Zone of bone organ fma:fma10483\\
	Bone compound				&Cranium				&Comparable to union of Skeletal system fma:fma23881 and subdivision of skeletal system fma:fma85544\\
	Tooth structure				&Dentes Permanentes		&Permanent teeth (fma:fma75152; TA2ID:913)\\
	Tooth						&Dens caninus			&Tooth fma:fma12516\\
	Tooth part					&Cuspis dentis			&fma:fma56481; TA2ID:925\\
	Phenotype					&Height, Sex			&											&Attributive\\							
	Anatomical Property			&Shape (Degree of morphological expression)	&Anatomical relation, e.g., Has\_shape relation	&Attributive\\
	Relative anatomical location&superior, lateral, medial, posterior	&Anatomical qualitative coordinate	&Relator\\
\bottomrule
\end{tabulary}
\end{table}
